\chapter*{Introduction}
\addcontentsline{toc}{chapter}{Introduction}
\chaptermark{Introduction}

This report provides a detailed account of my internship experience at Upteko, a company that is experiencing rapid growth and is characterized by its diverse and dynamic work environment. Upteko operates in a multitude of fields, including but not limited to hardware, software, simulation, fundraising, and professional events. This diversity offers a unique learning experience, presenting an opportunity to gain exposure to a wide range of disciplines and technologies. However, it also poses its own set of challenges, as the breadth of the company's operations can sometimes be overwhelming for trainees.
\\ \\
The report begins with a comprehensive presentation of the company, outlining its field of activity, history, legal and social model, economic model, and type of work organization. This is followed by a detailed description of the projects I was involved in during my internship, including the STM32 IMU project, the LogViewer project, and the Collision Avoidance SITL project. Each project section provides an overview of the tasks I undertook, the challenges I encountered, and the solutions I developed.
\\ \\
Throughout the report, I aim to highlight the knowledge and skills I acquired during my internship, as well as the insights I gained into the complexities and peculiarities of working in such a multifaceted environment. The report also includes a list of codes used in the projects, providing a technical perspective on the work carried out.